Bird beak's elaboration and innovation

### 2023-04-17 Analysis/07-Orthogonality_and_statistics.Rmd
Update 07-Orthogonality_and_statistics.Rmd
Working on PGLS (still buged)

library(tidyverse)
library(patchwork)

@@

ggsave("relative_EI_gg_style.pdf", plot=p, height=6, width=12)
```

@@

>>>>

# library(tidyverse)
library(patchwork)

@@

ggsave("../Manuscript/Figures/relative_EI_gg_style_unscaled.pdf", plot=p, height=6, width=12)
```

@@

## PGLS

```{r}
## Combining the model data as:
    ## centroid
    ## elaboration
    ## innovation
    ## elaboration order
    ## innovation order
    ## order_tree_elab/innov (from groups_median_EI$orders)
        # model_data[match(spp, model_data$species), "order_tree_elab"] <- groups_median_EI$orders[[1]][i]
    ## species names as row names
load("../Data/Processed/ploting_data.rda")
#load("../Data/Processed/ploting_data_superorder.rda")
load("../Data/Processed/ploting_data_order.rda")
load("../Data/Processed/groups_median_EI.rda")
load("../Data/Processed/shapespace.rda")

## Initialise the data
model_data <- data.frame("species" = rownames(shapespace), "orders" = shapespace$level2)
rownames(model_data) <- rownames(shapespace) 
model_data <- cbind(model_data,
                    centroid    = ploting_data$distances_to_centre[rownames(shapespace)],
                    elaboration_order = ploting_data_order$median_elaborations[rownames(shapespace)],
                    innovation_order  = ploting_data_order$median_innovations[rownames(shapespace)],
                    order_tree_elab = NA, order_tree_inno = NA)
## Attributing the median innov/elab value for each order
for(order in unique(model_data$orders)) {
    if(order != "") { # This is because a couple of species have no order
        group_num <- grep(order, names(groups_median_EI$orders$innovation)) ## FIX THAT!
        model_data[which(model_data$orders == order), "order_tree_elab"] <- groups_median_EI$orders$elaboration[group_num]
        model_data[which(model_data$orders == order), "order_tree_inno"] <- groups_median_EI$orders$innovation[group_num]
    }
}

consensus_tree <- ploting_data$consensus_tree
trees <- list(consensus_tree, consensus_tree)

clean_data <- model_data[!(apply(data, 1, function(x) any(is.na(x)))), ] ## NOT WORKING

run.models <- function(tree, data) {
    ## all predictors
    all_preds <- phylolm::phylolm(species ~ elaboration_order + innovation_order + order_tree_elab + order_tree_inno,
                         data = data, phy = tree, model = "lambda")
    ## macro predictors
    macro_preds <- phylolm::phylolm(species ~ elaboration_order + innovation_order,
                           data = data, phy = tree, model = "lambda")
    ## mega predictors
    mega_preds <- phylolm::phylolm(species ~ order_tree_elab + order_tree_inno,
                          data = data, phy = tree, model = "lambda")
    return(list(all = all_preds, macro = macro_preds, mega = mega_preds))
}

## Run 100 models
models_out <- lapply(trees, run.models, data = clean_data)

## Summarise them
summary_out <- lapply(models_out, lapply, summary)

## Tree is: phy <- read.tree("Prum_merge_hackett_stage2_1K_mcc.tree") (consensus - but get from distribution)
## Models are:

# # Model for all predictors
# mod1 <- phylolm(phylogeny ~ elaboration_order + innovation_order + order_tree_elab + order_tree_inno, data=model_data, phy=phy, model="lambda")
# summary(mod1)

```
